Replication of Gantman et al. 2024

### 2024-02-22 manuscript.qmd
working on regression-based artifact correction

```{r}
#| Libraries
#| include: false

library(readr)
library(dplyr)
library(jsonlite)
library(ggplot2)
```

```{r}
#| Download the data from the OSF

```

@@

```{r}
#| Check accuracy
#| include: false

@@

```{r}
#| label: Behavioral pop-out effect

@@

```{r}
#| label: model the GEE

@@

```{r}
#| Load eeg data
#| include: false

eeg_data <- read_csv("data/final/eeg.csv") %>%
  filter(!subject %in% excluded_subjects)
```

@@

```{r}
ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  facet_grid(electrode~category)+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal()+
  theme(panel.grid = element_blank())
```

>>>>

```{r}
#| label: Load libraries
#| include: false

library(readr)
library(dplyr)
library(jsonlite)
library(ggplot2)
library(osfr)
```

```{r}
#| label: Download the data from the OSF
osf_retrieve_node("ngtha") %>%
  osf_ls_files() %>%
  osf_download(path="data/final", conflicts="skip")
```

@@

```{r}
#| label: Check accuracy
#| include: false

@@

```{r}
#| label: fig-beh-pop-out

@@

```{r}
#| label: model the GEE
#| include: false

@@

```{r}
#| label: Load eeg data
#| include: false

eeg_data <- read_csv("data/final/eeg.csv", col_types = "cdcllcdlc") %>%
  filter(!subject %in% excluded_subjects)
```

@@

```{r}
#| label: fig-grand-averages
#| fig-width: 10
#| fig-height: 8
ggplot(grand_average, aes(x=t, y=M, color=is_word, linetype=word_category)) +
  geom_hline(yintercept = 0)+
  geom_vline(xintercept = 0)+
  geom_ribbon(aes(ymin=M-SE, ymax=M+SE, fill=is_word), alpha=0.2, color=NA)+
  geom_line()+
  scale_x_continuous(breaks=c(0,500, 1000))+
  facet_grid(electrode~category)+
  labs(x="Time since word onset (ms)", y="Voltage (uV)", color="Is word?", fill="Is word?", linetype="Word Category")+
  theme_minimal()+
  theme(panel.grid = element_blank())
```
